Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-16 report/report.tex
Emph -> Textbf

The primary contribution is an \emph{investigation into the rate of collision between map features in OSM}.
A program has taken an OSM dataset of the Stockholm area and assigned each road with standard withds according to swedish regulation.
It has then identified critical areas in the OSM dataset, where the paths are so wide that they collide with existing map features.
It has also identified how many of those areas can in theory be corrected by simple translation of the road vertices, without propagation of collision to other features.
Here, features are defined as the geometrical components that comprise the OSM map.
For the purpose of this report, features will refer mainly to roads and building footprints.

@@

The secondary contribution will be an \emph{assesment of the geometrical precision of OSM data} around the Stockholm area.
The positional accuracy will be estimated by comparing feature points between the OSM dataset and a reference dataset.
The positional accuracy will be needed to assess where road collisions occur and whether they can easily be corrected.

>>>>

The primary contribution is an \textbf{investigation into the rate of collision between map features in OSM}.
A program has taken an OSM dataset of the Stockholm area and assigned each road with standard withds according to swedish regulation.
It has then identified critical areas in the OSM dataset, where the paths are so wide that they collide with existing map features.
It has also identified how many of those areas can in theory be corrected by simple translation of the road vertices, without propagation of collision to other features.
Here, features are defined as the geometrical components that comprise the OSM map.
For the purpose of this report, features will refer mainly to roads and building footprints.

@@

The secondary contribution will be an \textbf{assesment of the geometrical precision of OSM data} around the Stockholm area.
The positional accuracy will be estimated by comparing feature points between the OSM dataset and a reference dataset.
The positional accuracy will be needed to assess where road collisions occur and whether they can easily be corrected.
